### 2021-08-31 response_to_review.Rmd

- p12 l11 add "to"

    - **done**

- p12 l12 which software is this? and which options for tour interactions are commonly available in other software with tour functionality such as XGobi, RGobi, tourr ?

    - **This has been done as much as possible, and the reference to rggobi is added**

@@

- p17 l41 mention Figure 17 here in the text

   - **done**

- p17 add "5.5 Historical applications" and briefly review other examples from the literature here; e.g., Koschat and Swayne seem to have used the tour for telecommunication data (see below)

    - **Phew! Tall order. Added a few examples to illustrate the range of applicability**

@@

    - **Fixed. Some of the problems are related to the template,. The bibtex files are complete so we hope that the typesetter can suitably make the complete citations.**

@@

- Section 2.3: "contains all the rotation to be between planes, not a particular basis in any plane". It maybe worth mentioning the difference between "interpolating frames" (interpolating projection frame A and B directly, which involves particular bases) vs. "interpolating planes" (between span(A) and span(B) ), and briefly discuss how the motion can be decomposed to motion of planes and within plane spin.

    - **done**

- Section 2.3: "The space of all tour *paths* is a high-dimensional torus..." --- All paths, all k-planes or all orthogonal k-frames? 
From the context it's not clear to me whether the space of all tour paths is a high-D torus. 
Consider giving some contexts/explanations to this statement?

    - **cited the original buja and asimov paper that states this, and you can see it from the torus shapes in Figure 18, too.**

### 2021-08-31 paper.Rmd
completely done with revision

Figure \ref{fig:interpolation-2d} shows tour paths of 2D projections of 6D data. The space of all tour paths is a high-dimensional torus, as represented by the gray points. The tour paths are shown in green and orange, and each dot indicates a projection in the sequence.  The plots in this figure could be considered to be a tour looking at itself, because each plot is a selected view from a tour of the torus with the paths overlaid.

@@

@@

## Model visualization

>>>>

Figure \ref{fig:interpolation-2d} shows tour paths of 2D projections of 6D data. The space of all tour paths is a high-dimensional torus [@Buja1986-sw], as represented by the gray points. (Note that the shape of the grey points matches that of the torus shapes discussed later and shown in Figure \ref{fig:geozoo}.) The tour paths are shown in green and orange, and each dot indicates a projection in the sequence.  The plots in this figure could be considered to be a tour looking at itself, because each plot is a selected view from a tour of the torus with the paths overlaid.

@@

Note that, in the application of tours to understanding neural networks by @Li2020-kg} in Section \@ref(models) also has a manually controlled tour based on selecting and dragging individual points that they call the "the data point mode".

@@

## Model visualization {#models}
